---
title: "lab2"
author: "Lillian Clark"
date: "9/6/2021"
output: pdf_document
---

(Spent most of lab trying to install `rstanarm`)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rstanarm)
library(bayesplot)
```

```{r}
bike <- read_csv("210830_bikecrash.csv")
```

```{r}
bike_new <- bike %>%
  mutate(crashes_pc = crashes / (pop / 100000),
         high_crash_cty = case_when(
           crashes_pc >= 60 ~ 1,
           TRUE ~ 0),
         high_crash_cty = as.factor(high_crash_cty))
```

```{r}
summary(bike_new$high_crash_cty)
summary(bike_new$pct_rural)

ggplot(bike_new, aes(x = high_crash_cty, y = pct_rural)) +
  geom_boxplot()
```

```{r}
m0 <- glm(high_crash_cty ~ I(pop/1000000) + pct_rural, data = bike_new, family = "binomial")
round(summary(m0)$coef, 6)
```

We use the estimate and standard error from a frequentist GLM as our prior for the intercept in our Bayesian regression.

```{r}
m1 <- stan_glm(high_crash_cty ~ I(pop/1000000) + pct_rural, 
                         data = bike_new, 
                         family = binomial(link = "logit"),
                         prior_intercept = normal(.995, .846),
                         prior = normal(0, 100, autoscale = T), 
                         chains = 2, iter = 10000, seed = 9763, 
                         prior_PD = F)
```

```{r}
prior_summary(m1)
color_scheme_set(c("darkblue", "darkred", "darkgray", 
                   "deepskyblue", "deeppink", "darkgreen"))
plot(m1, "trace")
plot(m1, "trace", pars = "pct_rural") +
  labs(title = "Trace plot: percent rural", 
       y = "Estimate", x = "Draw")
pp_check(m1, plotfun = "hist", nreps = 5) + 
  xlab("Crashes")
pp_check(m1) + 
  xlab("Crashes")
plot(m1, "acf_bar") +         # compare to "acf"
  labs(title = "ACF plots")
plot(m1, "dens_overlay")
round(as.data.frame(summary(m1)), 2)
```

```{r}
bike_new %>% 
  filter(county == "Durham")
durham <- posterior_predict(m1, 
                            newdata = data.frame(pop = 316739,
                                                 pct_rural = 6),
                            draws = 1000)
head(durham)
ggplot(as.data.frame(durham), aes(x = durham)) +
  geom_histogram(color = "darkblue", fill = "skyblue") +
  labs(x = "Posterior predictions", y = "Count") +
  geom_vline(xintercept = 340, color = "darkred", lwd = 2)
```

Is there evidence of an association between rurality and being a high-crash county, after adjusting for population? Explain, and quantify any variability in your estimates. Be sure to evaluate model convergence.

asks the beta coefficient for pct_rural
variability in beta_1

