---
title: "Survival Analysis: Game of Thrones"
author: "Lillian Clark"
date: "9/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rstanarm)
library(survminer)
library(survival)
```

```{r}
got <- read_csv("210927_got.csv")
```

Explore the data! Can you create a useful visualization that summarizes some aspects of the time-to-death in this dataset? Does there appear to be evidence of differential survival depending on certain characteristics (gender, royalty status, etc.)? What about potential confounders?

The following variables will be used:

duration_in_episodes: the number of episodes the character has made it to “so-far” through the end of Season 7 (we’re ignoring Season 8 because it’s hot trash)
is_dead: whether the character is dead
character_name: character name
royal: whether the character is a royal
house: which great house of Westeros the character belongs to (if any)
gender: gender of the character

```{r}
got <- got %>%
  select(character_name, gender, house, royal, duration_in_episodes, is_dead)
```


```{r}
ggsurvplot(survfit(Surv(duration_in_episodes, is_dead) ~ 1, data = got), 
     xlab = "Duration in Episodes", ylab = "Est. Survival Probability",
     conf.int = F)

ggsurvplot(survfit(Surv(duration_in_episodes, is_dead) ~ gender, data = got), 
     xlab = "Duration in Episodes", ylab = "Est. Survival Probability",
     ylim = c(0, 1),
     conf.int = T, censor = F)

ggsurvplot(survfit(Surv(duration_in_episodes, is_dead) ~ house, data = got), 
     xlab = "Duration in Episodes", ylab = "Est. Survival Probability",
     ylim = c(0, 1),
     conf.int = T, censor = F)

ggsurvplot(survfit(Surv(duration_in_episodes, is_dead) ~ royal, data = got), 
     xlab = "Duration in Episodes", ylab = "Est. Survival Probability",
     ylim = c(0, 1),
     conf.int = T, censor = F)

ggsurvplot(survfit(Surv(duration_in_episodes, is_dead) ~ gender + royal, data = got), 
     xlab = "Duration in Episodes", ylab = "Est. Survival Probability",
     ylim = c(0, 1),
     conf.int = T, censor = F)

survdiff(Surv(duration_in_episodes, is_dead) ~ royal, data = got)
survdiff(Surv(duration_in_episodes, is_dead) ~ gender, data = got)
survdiff(Surv(duration_in_episodes, is_dead) ~ house, data = got)
```
House seems like overfitting

```{r}
m1 <- stan_surv(Surv(duration_in_episodes, is_dead) ~ royal + gender, 
                data = got, basehaz = "weibull",
               prior = normal(autoscale = T),
               prior_intercept = normal(autoscale = T),
               prior_aux = cauchy(0, 5, autoscale = T),
               chains = 2, iter = 2000, seed = 123,
               prior_PD = F)

m2 <- stan_surv(Surv(duration_in_episodes, is_dead) ~ royal + gender, 
                data = got, basehaz = "weibull-aft",
               prior = normal(autoscale = T),
               prior_intercept = normal(autoscale = T),
               prior_aux = cauchy(0, 5, autoscale = T),
               chains = 2, iter = 2000, seed = 123,
               prior_PD = F)
```

```{r}
prior_summary(m1)
summary(m1)
round(as.data.frame(summary(m1)), 2)
round(as.data.frame(summary(m1))[,c(1, 3, 7)], 3)
plot(m1, plotfun = "basehaz")
ps_check(m1)
plot(m1, "dens_overlay")
plot(m1, "trace")

prior_summary(m2)
summary(m2)
round(as.data.frame(summary(m2)), 2)
round(as.data.frame(summary(m2))[,c(1, 3, 7)], 3)
plot(m2, plotfun = "basehaz")
ps_check(m2)
plot(m2, "dens_overlay")
plot(m2, "trace")
```



